An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-30 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
added some more text about performance assessment

@@

\subsection{Random Initialization Versus Cost-Optimal Initialization}

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_OriginalCost_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:allsolutions} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations for all three objectives (top left) and each combination of two objectives on the lazio\_4\_1 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_New_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:onlynondominated} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations on the uncorrelated\_4 instance.}
\end{figure}

>>>>

In terms of performance assessment, we present both visual comparisons of the final populations as well as statistical results. For the statistical results, the hypervolume indicator was also used as quality measure of the final populations as it is the only known unary quality indicator  which is a refinement of the Pareto dominance relation and therefore has important theoretical properties: whenever a set of solutions dominates another set, also the hypervolume value is higher; on the contrary, if the hypervolume indicator value of a set A is worse than for set B, we know that B cannot dominate A \citep{ztlf2003a,ztb2010a}. In order to compare algorithms with respect to their hypervolume indicator values, we use both box plots\footnote{As implemented in MATLAB R2008b.} and the Wilcoxon rank sum test\footnote{As implemented in the statistical programming language R, version 2.1.3.0.}.

@@

\subsection{Random Initialization Versus Cost-Optimal Initialization}
In order to see the impact of the two different initialization schemes \emph{random} and \emph{cost-optimal}, we performed 10 runs of HypE with both initialization schemes for 2,000 generations and a population size of 50 as above. Figure~\ref{fig:randVsCostOriginal} shows the resulting non-dominated solutions of the final populations. Surprisingly, the cost-optimal initialization could not produce other solutions than the cost-optimal one itself. \TODO{However, what can be seen is that the ...}

Boxplots can be found in Fig.~\ref{fig:costVsRandBoxPlots} ...

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_OriginalCost_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostOriginal} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations for all three objectives (top left) and each combination of two objectives on the lazio\_4\_1 instance.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.75\columnwidth]{../experiments/randVsCost/randVsCost_ns4_1_New_2000gens.eps}
	\vspace{-1em}
	\caption{\label{fig:randVsCostNew} Comparison between the random initialization ($\circ$) and the cost-optimal one ($\times$). Shown are the non-dominated solutions in the final populations of 10 independent HypE runs with population size 50 after 2000 generations on the uncorrelated\_4 instance.}
\end{figure}
